CONEM2024-0025\\ ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
percentage

$e_{p\sigma_q}$ is the product lead time billing equivalent to product $p$ on the criterion $\sigma_q$;

@@

$b_p$ is the billing of product $p$;

$lt_p$ is the lead time of product $p$;

$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing of product $p$;

$w_{pc}$ is the weight of the product $p$ according to criterion $c$;

$wb$ is the weight of criterion billing.

$wlt$ is the weight of criterion lead time.

$w_{c}$ is the weight of criterion $c$.

>>>>

$e_{p\sigma_q}$ is the product lead time billing weight percentage equivalent to product $p$ on the criterion $\sigma_q$;

@@

$b_p$ is the billing weight percentage of product $p$;

$lt_p$ is the lead time weight percentage of product $p$;

$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing weight percentage of product $p$;

$w_{pc}$ is the weight percentage of the product $p$ according to criterion $c$;

$wb$ is the weight percentage of criterion billing.

$wlt$ is the weight percentage of criterion lead time.

$w_{c}$ is the weight percentage of criterion $c$.
